Manuscript for Markup Language course - Using bayesian statistics to prove

### 2022-05-11 manuscript_inan.Rmd
fixed bug in text that made it unable to knit to pdf and added pdf

---
title: Manuscript for Markup Language course - Using bayesian statistics to prove
  a point
author: "Inan Bostanci"
date: "1/15/2022"
output:
  html_document: default
  pdf_document: default
---

@@

## 4.5 Testing the hypotheses
Finally, I will test my claims about the effect of protein and GDP on height in several ways. First, I will test the hypothesis that the effect of protein is larger than the effect of GDP using the BF with standardized coefficients (denoted by the subscript $stz; H_2: \beta_{1stz} > \beta_{2stz}; H_u: \beta_{1stz} ≤ \beta_{2stz}$). Next, I will use the MCMC-method to model the data with a one-predictor-model using just the protein or GDP-variable. I will then compare all three models by means of the DIC, which is a function of the model’s fit and complexity. I expect the DIC of the model containing protein only to be lower than the DIC of the model containing GDP only. Furthermore, I expect the model containing protein only to have about the same DIC as the model containing both parameters. This is because I expect the fit to be about as good, since I believe that protein is by far the stronger predictor, and the complexity to be just minorly different, since the full model only has one added parameter given a large sample size.

>>>>

---
title: Manuscript for Markup Language course - Using bayesian statistics to prove
  a point
author: "Inan Bostanci"
date: "1/15/2022"
output:
  pdf_document: default
  html_document: default
---

@@

## 4.5 Testing the hypotheses
Finally, I will test my claims about the effect of protein and GDP on height in several ways. First, I will test the hypothesis that the effect of protein is larger than the effect of GDP using the BF with standardized coefficients (denoted by the subscript $stz; H_2: \beta_{1stz} > \beta_{2stz}; H_u: \beta_{1stz} \le \beta_{2stz}$). Next, I will use the MCMC-method to model the data with a one-predictor-model using just the protein or GDP-variable. I will then compare all three models by means of the DIC, which is a function of the model’s fit and complexity. I expect the DIC of the model containing protein only to be lower than the DIC of the model containing GDP only. Furthermore, I expect the model containing protein only to have about the same DIC as the model containing both parameters. This is because I expect the fit to be about as good, since I believe that protein is by far the stronger predictor, and the complexity to be just minorly different, since the full model only has one added parameter given a large sample size.
